### 2022-08-21 manuscript.Rmd
Add text for control analysis

```{r, control_analysis}
# (Re-)do the actual model fitting if requested
if (run$mixed_models_control) {

@@

>>>>

```{r, control_analysis}
# (Re-)do the actual model fitting if requested
if (run$control_analysis) {

@@

There are at least two important alternative explanations for our finding that semantic information instantly affects early ERP responses.
First, differences in the P1 and/or N170 components might be driven by low-level visual differences between object images rather than by our experimental manipulation (matching versus non-matching keywords in the insight phase).
We ruled out this alternative explanation by counter-balancing the assignment of objects to conditions across participants, meaning that the same visual object entererd the analysis in both conditions on an approximately equal number of trials, barring differences in participants' classification of the object and differences in the number of rejected EEG trials (see Materials and Methods).
Furthermore, we did not detect reliable differences between the two conditions in the pre-insight phase, that is, before any keywords had been presented.
It therefore seems unlikely that low-level differences could account for the tentative effects of semantic information reported above.

Second, there is an alternative explanation specifically for the effects observed in the insight phase, when the objects were presented together with matching or non-matching keywords.
Namely, the early difference in the N170 component might in fact not be due to semantic information changing the processing of objects in the semantically informed condition (as we had hypothesized), but rather a mismatch response to the objects in the semantically naive condition.
In this condition, objects were presented with non-matching keywords that led participants to indicate that they did not understand what kind of object they were viewing.
These non-matching keywords might have primed participants to expect an approximate set of visual features that, once the actual object was displayed, did not obtain and therefore provoked a fast and strong brain response within the first 200 ms.
However, in a control analysis for this alternative explanation, we could show that the N170 effect in the insight phase does not depend on the semantically naive condition.
For this control analysis, we again used the semantically informed condition as defined above, but contrasted it against a different control condition.
Namely, we used those objects that were presented with matching keywords (as in the semantically informed condition) but for which participants failed to capitalize on the keywords and rather indicated that they still did not know what kind of object they were viewing (a kind of "failed insight").
This was the case for an average of `r mean(objects_per_condition$Exclude_informed)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
Contrasting the semantically informed condition and the failed insight conditions, we again observed a significant enlarged (i.e., more negative) N170 component during semantically informed perception, $b$ = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N170" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
Likewise, the reduction of the N400 was also observed in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N400" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`.
This adds credibility to the notion that these effects are specific to those objects for which participants experienced a moment of semantic insight.
